Women in Film

### 2017-07-17 draft_post.Rmd
Working on some example texts

example_text <- example_words %>%
    mutate(pronoun = pronouns,
           phrase = str_c(pronoun, word, sep = " ")) %>%
    pull(phrase) %>%
    map_df(function(x) all_lines %>%
               filter(str_detect(text, x)) %>%
               sample_n(1) %>%
               select(text)) %>%
    bind_cols(example_words) %>%
    select(word, text)

@@

There are some words that writers who are men and women are more likely to use, no matter what kind of character they are writing. In the upper right quadrant, we find the words that writers who are women are more likely to use. Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst into places. And lots of flinging! The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters. Writers who are men are more likely to write characters who react, clutch, dive, shout, ducks, and emerge from places.

>>>>

example_text <- example_words %>%
    mutate(pronoun = pronouns,
           phrase = str_c(pronoun, word, sep = " ")) %>%
    pull(phrase) %>%
    map_df(function(x) all_lines %>%
               filter(nchar(text) < 140,
                      str_detect(text, x)) %>%
               sample_n(1) %>%
               select(text)) %>%
    bind_cols(example_words) %>%
    select(word, text)

@@

There are some words that writers who are men and women are more likely to use, no matter what kind of character they are writing. In the upper right quadrant, we find the words that writers who are women are more likely to use. Writers who are women are more likely to write characters who sing, love, shift, sink into things, and burst out or into places. And lots of flinging! The lower left quadrant shows the words that writers who are men are more likely to use, for both male and female characters. Writers who are men are more likely to write characters who react, clutch, dive, shout, ducks, and emerge from places.
